prolfqua - A Comprehensive R-package for Proteomics Differential Expression Analysis

### 2022-06-01 inst/MyArticle/paper.Rmd
Add quote
Remove dot in title

---
title: prolfqua - A Comprehensive R-package for Proteomics Differential Expression Analysis.
author: 
  - Witold E. Wolski $^{\dagger\ddagger}$^[[Functional Genomics Center Zurich (FGCZ)](https://fgcz.ch) - [Swiss Federal Institute of Technology in Zurich](https://ethz.ch) \| [University of Zurich](https://uzh.ch); Winterthurerstrasse 190, CH-8057 Zurich, Switzerland. $^\ddagger$[Swiss Institute of Bioinformatics (SIB)](https://www.sib.swiss/) $^\dagger$Correspondence \texttt{wew@fgcz.ethz.ch}]
  - Paolo Nanni$^{\ast}$
  - Jonas Grossmann$^{\ast\ddagger}$
  - Maria d'Errico$^{\ast\ddagger}$
  - Ralph Schlapbach$^{\ast}$
  - Christian Panse$^{\ast\ddagger}$
output: 
  bookdown::pdf_document2:
      toc: true
      toc_appendix: false
      toc_bib: false
bibliography: bibliography.bib
editor_options: 
  chunk_output_type: console
abstract: |
    Protein mass spectrometry is widely used for quantitative proteomics studies, relative protein quantification, and differential expression analysis of proteins. Nevertheless, there is a need for a flexible and easy-to-use application programming interface in R that transparently supports a variety of well principled statistical procedures. The `r BiocStyle::Githubpkg("fgcz/prolfqua")` package can model simple experimental designs with a single explanatory variable and complex experiments with multiple factors and hypothesis testing. It integrates essential steps of the mass spectrometry-based differential expression analysis workflow: quality control, data normalization, protein aggregation, statistical modeling, hypothesis testing, and sample size estimation. The application programmer interface strives to be clear,  predictable, discoverable, and consistent to make proteomics data analysis easy and exciting. 
     Furthermore, the package implements benchmark functionality that can help to compare data acquisition, data preprocessing, or data modeling methods using a gold standard dataset. Finally, we show that the implemented methods allow sensitive and specific differential expression analysis. 
     The R package is available on github https://github.com/fgcz/prolfqua.
urlcolor: blue
---

@@

>>>>

---
title: prolfqua - A Comprehensive R-package for Proteomics Differential Expression Analysis
author: 
  - Witold E. Wolski $^{\dagger\ddagger}$^[[Functional Genomics Center Zurich (FGCZ)](https://fgcz.ch) - [Swiss Federal Institute of Technology in Zurich](https://ethz.ch) \| [University of Zurich](https://uzh.ch); Winterthurerstrasse 190, CH-8057 Zurich, Switzerland. $^\ddagger$[Swiss Institute of Bioinformatics (SIB)](https://www.sib.swiss/) $^\dagger$Correspondence \texttt{wew@fgcz.ethz.ch}]
  - Paolo Nanni$^{\ast}$
  - Jonas Grossmann$^{\ast\ddagger}$
  - Maria d'Errico$^{\ast\ddagger}$
  - Ralph Schlapbach$^{\ast}$
  - Christian Panse$^{\ast\ddagger}$
output: 
  bookdown::pdf_document2:
      toc: true
      toc_appendix: false
      toc_bib: false
bibliography: bibliography.bib
editor_options: 
  chunk_output_type: console
abstract: |
    Protein mass spectrometry is widely used for quantitative proteomics studies, relative protein quantification, and differential expression analysis of proteins. Nevertheless, there is a need for a flexible and easy-to-use application programming interface in R that transparently supports a variety of well principled statistical procedures. The `r BiocStyle::Githubpkg("fgcz/prolfqua")` package can model simple experimental designs with a single explanatory variable and complex experiments with multiple factors and hypothesis testing. It integrates essential steps of the mass spectrometry-based differential expression analysis workflow: quality control, data normalization, protein aggregation, statistical modeling, hypothesis testing, and sample size estimation. The application programmer interface strives to be clear,  predictable, discoverable, and consistent to make proteomics data analysis easy and exciting. 
     Furthermore, the package implements benchmark functionality that can help to compare data acquisition, data preprocessing, or data modeling methods using a gold standard dataset. Finally, we show that the implemented methods allow sensitive and specific differential expression analysis. 
     The R package is available on github https://github.com/fgcz/prolfqua.
urlcolor: blue
---

@@

 \begin{quote}
``Es ist nicht das Wissen, sondern das Lernen, nicht das Besitzen, sondern das Erwerben, nicht das Dasein, sondern das Hinkommen, was den größten Genuß gewährt.''

Carl Friedrich Gauß
 \end{quote}
